A* with Fast and Tight Heuristic in Road Networks

### 2020-08-13 paper/ch_potentials.tex
graph preliminaries

In this paper, we consider a setup with a preprocessing phase and a query phase.
The preprocessing phase can be slow and computes auxiliary data that can be used in the query phase, which should be fast.
The input to the preprocessing phase is the graph weighted with lower bound weights $w_\ell$.
The source/origin $s$ and target/goal $t$ of the path and the actual edge weights $w_q$ are the input to the query phase.
We require that $w_q(e)\ge w_\ell(e)$ for all edges $e$.
In the query phase, the path is computed.
%
Street networks of continental scale have many millions of nodes.
% While the preprocessing phase may be slow, it must eventually finish.
On graphs of this size, quadratic preprocessing time is prohibitive.

In this paper, we consider an algorithm, where the query phase mostly consists of an A* search.
The preprocessing phase computes auxiliary data to efficiently evaluate the heuristic.
Our setup is very similar to the well-known ALT technique~\cite{gh-cspas-05,DBLP:conf/wea/DellingW07}.
We call our algorithm CH-Potentials, as it combines ideas from Contraction Hierarchies (CH)~\cite{gssv-erlrn-12} with A* heuristics, also called potentials in~\cite{gh-cspas-05}.

>>>>

In this paper, we consider a setup with a preprocessing phase and a query phase.
The preprocessing phase can be slow and computes auxiliary data that can be used in the query phase, which should be fast.
The input to the preprocessing phase is a directed graph $G=(V,E)$ weighted with lower bound weights $w_\ell$.
The source/origin $s$ and target/goal $t$ of the path and the actual edge weights $w_q$ are the input to the query phase.
We require that $w_q(e)\ge w_\ell(e)$ for all edges $e \in E$.
In the query phase, the path is computed.
%
Street networks of continental scale have many millions of nodes.
% While the preprocessing phase may be slow, it must eventually finish.
On graphs of this size, quadratic preprocessing time is prohibitive.

In this paper, we consider an algorithm, where the query phase mostly consists of an A* search.
The preprocessing phase computes auxiliary data to efficiently evaluate the heuristic.
Our setup is very similar to the well-known ALT technique~\cite{gh-cspas-05,DBLP:conf/wea/DellingW07}.
We call our algorithm \emph{CH-Potentials}, as it combines ideas from Contraction Hierarchies (CH)~\cite{gssv-erlrn-12} with A* heuristics, also called potentials in~\cite{gh-cspas-05}.
